---
title: "Intro to models"
author: "Ashlee"
date: "4/28/2022"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../Output/')
```

# Introduction
Today we will have a basic introduction to working with models. 
Intro to basic linear modeling
Viewing results in base R, broom, and modelsummary
Running many models at the same time with purrr
Intro to tidy models

# Libraries 
```{r}
library(tidyverse)
library(here)
library(palmerpenguins)
library(broom)
library(performance)
library(modelsummary)
library(tidymodels)
```
Anatomy of basic linear model 
To run a simple linear model you use the following formula:
```{r}
#mod <- lm(y~m, data = df)
```
lm = linear model, y = dependent variable, x = independent variable(s), df = dataframe.
You read this as y is a function of x

Model the penguin dataset
```{r}
# Linear model of Bill depth ~ Bill length by species
Peng_mod<-lm(bill_length_mm ~ bill_depth_mm*species, data = penguins)
```

Always check assumptions with performance 
```{r check}
check_model(Peng_mod) # check assumptions of an lm model
```
View Results: base R
ANOVA Table 
```{r}
anova(Peng_mod)
summary(Peng_mod)
```
View Results with broom 
```{r}
# Tidy gives you coefficients
coeffs<-tidy(Peng_mod) # just put tidy() around it
coeffs


# Glance extracts R-squared, AICs, etc of the model 
# tidy r2, etc
results<-glance(Peng_mod) 
results

# Augment adds residuals and predicted values to original data 
# tidy residuals, etc
resid_fitted<-augment(Peng_mod)
resid_fitted
```
Results in {modelsummary}
* creates tables and plots to summarize statistical models and data in R.

* modelsummary includes two families of functions:

Model Summary
modelsummary: Regression tables with side-by-side models.
modelsummary_wide: Regression tables for categorical response models or grouped coefficients.
modelplot: Coefficient plots.

Data Summary
datasummary: Powerful tool to create (multi-level) cross-tabs and data summaries.
datasummary_balance: Balance tables with subgroup statistics and difference in means (aka “Table 1”).
datasummary_correlation: Correlation tables.
datasummary_skim: Quick overview (“skim”) of a dataset.
datasummary_df: Turn dataframes into nice tables with titles, notes, etc.

Want to compare two penguin models 
```{r}
# New model
Peng_mod_noX<-lm(bill_length_mm ~ bill_depth_mm, data = penguins)
#Make a list of models and name them
models<-list("Model with interaction" = Peng_mod,
             "Model with no interaction" = Peng_mod_noX)
#Save the results as a .docx
modelsummary(models, output = here("Week_13","Output","table.docx"))
```

Modelplot 
Canned coefficient modelplots
```{r Modelplot}
library(wesanderson)
modelplot(models) +
    labs(x = 'Coefficients', 
         y = 'Term names') +
    scale_color_manual(values = wes_palette('Darjeeling1'))

```
Many Models with purr, dplyr, and broom 

Compare lots of different models at the same time and view results. 
An example using purr with many lists 
```{r}
 models<- penguins %>%
  ungroup()%>% # the penguin data are grouped so we need to ungroup them
    nest(-species) %>%  # nest all the data by species. creates a list/ tibble for all species 
  mutate(fit = map(data, ~lm(bill_length_mm~body_mass_g,data = .)))
## creates model output for each individual species. Use map bc same thing over and over again 
models

models$fit # shows you each of the 3 models

# View the results. First, let's mutate the models list so that we have a tidy coefficient dataframe (using tidy()) and a tidy model results dataframe (using glance())
 results<-models %>%
   mutate(coeffs = map(fit, tidy), # look at the coefficients
          modelresults = map(fit, glance))  %>% # R2 and others
   select(species, coeffs, modelresults) %>% # only keep the results
   unnest() # put it back in a dataframe and specify which columns to unnest

results # view the results 
```

Tidymodels 
Uses layering to create models. Start by specifying functional form 
```{r}
linear_reg() # creating linear regression 
```

We need to set the engine for what type of linear regression we are modeling. 
```{r reg}
lm_mod<-linear_reg() %>%
  set_engine("lm") %>%
  fit(bill_length_mm ~ bill_depth_mm*species, data = penguins) %>%  # next need to add model fit 
  tidy() %>% ## need to add tidy 
  ggplot()+
    geom_point(aes(x = term, y = estimate))+
    geom_errorbar(aes(x = term, ymin = estimate-std.error,
                      ymax = estimate+std.error), width = 0.1 )+
  coord_flip()

lm_mod
```
 
