---
title: "Mario Cart Championships"
author: "Ashlee Ochoa"
date: "3/10/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: journal
 
---

```{r setup, include=FALSE, fig.path = '../Output/', warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

I will be using the Mario Kart data from [Tidy Tuesday 2021-05-25](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-05-25/readme.md) for our homework assignment on creating a good plot and bad plot.  

# Loading Libraries 

The libraries I will be using to complete the assignment. 
```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(here)
library(tidytuesdayR)
library(tint)
library(patchwork)
```

# Loading Data

The Tidy Tuesday data I will be plotting. 
```{r, message=FALSE, warning=FALSE, fig.path = '../Data/'}


records <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/records.csv')
drivers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/drivers.csv')



```
# Filtering out Data

Wrangling selected data. 
```{r, warning=FALSE, message=FALSE, fig.path = '../Data/'}
remove <- c("Koopa Troopa Beach", "Moo Moo Farm", "Kalimari Desert", "Toad's Turnpike", "Banshee Boardwalk", "Rainbow Road", "Royal Raceway", "Choco Mountain", "Bowser's Castle", "Sherbet Land")

WR <- records %>% 
  filter(type== "Single Lap", # filtering selected data 
         shortcut == "No",
         system_played == "NTSC") %>% 
   filter(!track %in% remove) #%>% ## removing specific track names 
 # drop_na()
  
#remove <- c("Koopa Troopa Beach", "Moo Moo Farm", "Kalimari Desert", "Toad's Turnpike", "Banshee Boardwalk", "Rainbow Road", "Royal Raceway", "Choco Mountain", "Bowser's Castle", "Sherbet Land")

  
Driver <- drivers %>% 
  filter(nation == "USA") %>% # selecting only from the US
  drop_na()

DataTable <- full_join(WR, Driver) %>% # joining both data sets 
  drop_na()

#Category <- c("Lugi Raceway", "Moo Moo Farm", "Koopa Troopa Beach", "Kalimari Desert")
```

# Plotting the Data 

Plotting the race tracks against the time (in seconds) that it took each drivers to complete a single lap filled in by the players leader board position. 

* All players from the US
* All players used NTSC system
* Non- Short cut record 
* Single lap 

## Good Plot 

Factors of a good plot 

* Distinct axis titles 
* Creativity 
* Clear labeling 

Possible correction

 * Track name position 
 
```{r GoodPlot, message=FALSE, warning=FALSE, fig.align='center', fig.path = '../Output/'}

 ggplot(data = DataTable, aes(x= track, y=time, # plotting of selected data 
                             color = position))+
  #geom_linerange(aes(y=position, xmin=0, xmax=50, color=position), size=2, alpha=0.5) +
  geom_col(aes(y = Inf), fill = "pink") + 
  geom_point(size =1.5, alpha = 1.0) + # altering point elements 
  scale_color_viridis_b() + # altering color of position 
  coord_polar(theta = "y") + # gives a circular element 
  labs(x = "Track Name", y= "Time (s)", # labeling 
       title= "Mario Kart World Record",
       color = "Leader Board Position") +
  #geom_text(vjust = -1) +
  scale_x_discrete(expand = expand_scale(add = c(5,0))) +
 # scale_color_brewer("Set3") +
    theme_tint()

```

## Bad Plot 

Ways in which this label is misleading and incorrect 

* No clear labels or units 
* Bad choice of graph 
* No clear context or emphasis on what is being depicted- No direction 
* Measure of uncertainty is unclear 
* Very __Plain__

```{r BadPlot, message=FALSE, warning=FALSE, fig.align='center', fig.path = '../Output/'}
DataTable1 <- DataTable #assigning new name to data set 
ggplot(data = DataTable1, aes(x= track, y=time,
                             color = position)) +
  geom_boxplot() +  
    labs(x = "Track Name", y= "Time (s)",
       title= "Mario Kart World Record") +
  theme_void()
```


```{r message=FALSE, warning=FALSE}
```{r message=FALSE, warning=FALSE}