---
title: "Functions Lab"
author: "Ashlee"
date: "3/17/2022"
output: 
  html_document:
    theme: darkly

---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../Output/')
```

# Introduction 
For todays lab assignment I will be using the site.characteristics.data from week 5 to create a function. 

# Loading Libraries 
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(here)
```
# Loading Data
```{r, warning=FALSE, message=FALSE}
Data <- read_csv(here("Week_5", "Data", "site.characteristics.data.csv"))
```
# Wrangling 
```{r}
Data1 <- Data %>% 
  pivot_wider(names_from = parameter.measured, ### pivot wider 
              values_from = values)
  

Data2 <- Data %>% 
  filter(name== "Creepy Tree" | name == "Public Beach" | name == "Manava") %>% ## filtering for three names 
  filter(parameter.measured =="temp" | parameter.measured == "coral.cover" | parameter.measured == "algal.cover" | parameter.measured == "substrate.cover") ## filtering parameters 
```
# Plotting 
The set function created titled "myplot" and the outputs are saved as "function" and "function2" respectively.

```{r function, warning=FALSE, message=FALSE}
myplot <- function(data, x, y) { ### creating a function based off the plotting details  
#Data2 %>% 
  ggplot(data, aes(x = {{x}}, y = {{y}}, fill= name)) + ### curly curly for x and y 
  geom_col() +
 # labs(x = "Parameter", y= "Values",
   #    title = "Values of Parameters",
    #   fill = "Name")+
    theme_classic()
  
}

#ggsave(here("Week_8", "Output", "function.png"))

myplot(data= Data2, x = parameter.measured, y = values) + ## selecting x and y values 
    labs(x = "Parameter", y= "Values", ## modifying the titles 
       title = "Values of Parameters",
       fill = "Name")
```


An example of the function with the x and y switched 
```{r function2, warning=FALSE, message=FALSE}
myplot(data = Data2, x= values, y= parameter.measured) + ## swapping the x and y values 
    labs(x = "Values", y= "Parameters", ## altering the axis labels 
       title = "Values of Parameters",
       fill = "Name")
#ggsave(here("Week_8", "Output", "function2.png"))
```
# An example of another function 

Using "sum" to add values together 
```{r}
sum <- function(x, y) {  ##function based off a sum value 
  sum <- x+y  
  return(sum) 
}

sum(x=76, y= 89)
```
```{r}
sum(4, 25)
```

